---
title: "Endoscopy OPCS_4 code extraction"
author: "Sebastian Zeki"
date: "92/01/2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Aim


**eg** The script aims to extract OPCS_4 codes from written endoscopy reports


```{r Aim}
```



## Methods


**$\color{red}{\text{E.Define the Dates}}$.**

The manually extracted codes were extracted for all endoscopies performed by two endoscopists where the primary ICD-10 code was Barrett's oesophagus (K227) between the 1st June 2016 and 1st June 2017 from the centralised electonic patient record. The manually coded OPCS-4 code was available via Klikview and was downloaded for the same time period. The two datasets were merged into a single dataset by date and hospital number. EndoMineR (REF) was used to extract information from this primary dataset. The function within EndoMineR (OPCS-4) was run to extract primary codes from the dataset



```{r Acquisition}
library(DiagrammeR)
library(CodeDepends)
library(tidyverse)
library(readxl)
library(EndoMineR)
library(dplyr)
library(kableExtra)
library(EndoMineR)
######################################### Data acquisiton, cleaning and accordionisation######################################### 
#EndoAcquisitionAndCleaning.R

######################################### Data acquisiton######################################### 
#This is where the data is imported
ManualOPCS_4<-read_excel("S:\\Gastroenterology\\Seb\\R\\Data\\OPCS_4_Extraction\\TB_ALLPATID_20190102_110922.xls")
WholeData<-read_excel("S:\\Gastroenterology\\Seb\\R\\Data\\SelfAudit\\OrigEndoscopyFrom2007ToApr1_2017\\GSTT_TCR2232_AllEndoscopyProcedure_since_2007.xlsx")


######################################### Data merging######################################### 
#This is where external datasets are merged with the current dataset. This can be done after cleaning as well especially if you need to clean dates etc.
######################################### Data cleaning######################################### 


names(WholeData)<-c("PatientID",  "NHSno", "PatientName", "birthdaynum","birthmonthnum" ,"birthyearnum" ,"Endo_ResultName", "Endo_ResultPerformed", "Endo_ResultEntered", "Endo_ResultText", "Histo_ResultName", "Histo_ResultPerformed", "Histo_ResultEntered", "Histo_ResultText")

#Remove the first row if necessary
#WholeData<-subset(WholeData,!(is.na(WholeData["Endo_ResultName"])))



#Use Extractor2 as delimiters are organised in a non-consistent way:
WholeData$Endo_ResultText<-gsub('2nd Endoscopist:','Second endoscopist:',
                           WholeData$Endo_ResultText)
Self<-WholeData
EndoscTree<-list("Patient Name:","Date of Birth:","Hospital Number:","Date of Procedure:","Endoscopist:","Second endoscopist:",
                 "Referring Physician:","General Practicioner:","Nurses:",
                 "Medications:","Instrument:","Extent of Exam:","Visualization:","Tolerance:","Complications:","Co-morbidity:",
                 "INDICATIONS FOR EXAMINATION","PROCEDURE PERFORMED",
                 "FINDINGS","ENDOSCOPIC DIAGNOSIS","RECOMMENDATIONS","COMMENTS","BIOPSIES","OPCS4 Code:","Signature:","")
for(i in 1:(length(EndoscTree)-1)) {
  Self<-Extractor2(Self,'Endo_ResultText',as.character(EndoscTree[i]),
                   as.character(EndoscTree[i+1]),as.character(EndoscTree[i]))
}


HistolTree<-c("NATURE OF SPECIMEN:","CLINICAL DETAILS","MACROSCOPICAL DESCRIPTION","HISTOLOGY",
              "DIAGNOSIS","")
for(i in 1:(length(HistolTree)-1)) {
  Self<-Extractor2(Self,"Histo_ResultText",as.character(HistolTree[i]),
                   as.character(HistolTree[i+1]),as.character(HistolTree[i]))
}




Self<-EndoscEndoscopist(Self,'Endoscopist')
Self$Endoscopist<-gsub("Second","",Self$Endoscopist)
Self<-EndoscMeds(Self,'Medications')
Self<-EndoscInstrument(Self,'Instrument')
Self<-EndoscIndications(Self,'INDICATIONSFOREXAMINATION')
Self<-EndoscProcPerformed(Self,'PROCEDUREPERFORMED')


Self<-HistolDx(Self,"HISTOLOGY")
Self<-HistolExtrapolDx(Self,"Dx_Simplified","[Hh]yperplastic")

######################################### Data merging######################################### 
#Done in the source file
```

```{r Forking}
######################################### Data forking (filtering and subsetting) #########################
#Dataset1- The Endoscopy reports
Self$Endoscopist <- str_replace(Self$Endoscopist, ":", "")

#Select procedure type
SelfOGD<-Self[grepl(".*Gastroscopy.*",Self$PROCEDUREPERFORMED),]

#Select endoscopist
SelfOGD_Dunn<-Self[grepl("Dunn",Self$Endoscopist),]


#Dataset2- The Klikview reports
selected<-ManualOPCS_4%>%select("Prim Proc Code & Description","2nd Proc Code","Trust ID","Surname","Forename","Consultant","Admission Date","Prim Diag Code & Description")

#Clean the column names:
library(janitor)
selectedClean<-clean_names(selected,"snake")

#Rename the column names so can do the dataset merge
library(writexl)
write_xlsx(selectedClean, "S:\\Gastroenterology\\selectedClean.xlsx")
write_xlsx(SelfOGD_Dunn, "S:\\Gastroenterology\\SelfOGD_Dunn.xlsx")

library(readxl)

selectedClean<-read_excel("/home/rstudio/GenDev/DevFiles/EndoMineRFunctionDev/selectedClean.xlsx")
SelfOGD_Dunn<-read_excel("/home/rstudio/GenDev/DevFiles/EndoMineRFunctionDev/SelfOGD_Dunn.xlsx")

#Get the events
SelfOGD_Dunn<-Barretts_EventType(SelfOGD_Dunn,'HISTOLOGY','PROCEDUREPERFORMED','FINDINGS','INDICATIONSFOREXAMINATION')

#Make the date columns consistent
SelfOGD_Dunn<-SelfOGD_Dunn %>% rename(
 trust_id = "PatientID",
 admission_date = "Endo_ResultEntered")
selectedClean$admission_date<-as.Date(selectedClean$admission_date)
SelfOGD_Dunn$admission_date<-as.Date(SelfOGD_Dunn$admission_date)


Total<-merge(selectedClean,SelfOGD_Dunn,by=c("trust_id","admission_date"))

Total<-Total%>%select(trust_id,admission_date,prim_proc_code_description,x2nd_proc_code,Endo_ResultText,EVENT)
#Now just select the relevant total columns so that we have a clean and precise dataset:


```
############################## Start here ####################################


```{r DataLinkage}
merge()


```

```{r DataPreparation}
#Now have to get ready to do a demographics table:
#Age at diagnosis
#Sex
```

```{r PrelimAnalysisHRM}
```



```{r VarDiagram}
#### Documenting the sets 
# nodes <- create_node_df(n=6, 
#                         nodes=c("ImpAll", "AllBravo", "NegativeImpedance","MyBravoFromNegativeImpedance","MyBravoFromNegativeImpedancePOSITIVE_BRAVO","MyBravoFromNegativeImpedanceNEGATTIVE_BRAVO"),
#                         label=c(paste0("ImpAll: ",nrow(ImpAll)), stringr::str_wrap(paste0("All BRAVO: ",nrow(AllBravo)),10), stringr::str_wrap(paste0("Negative Impedance: ",nrow(NegativeImpedance)),10),
#                                 stringr::str_wrap(paste0("MyBravo (Negative Impedance):",nrow(MyBravoFromNegativeImpedance)),10),
#                                 stringr::str_wrap(paste0("Positive BRAVO:",nrow(MyBravoFromNegativeImpedancePOSITIVE_BRAVO)),10),
#                                 stringr::str_wrap(paste0("Negative BRAVO: ",nrow(MyBravoFromNegativeImpedanceNEGATTIVE_BRAVO)),10)),
#                         shape = "rectangle",
#                         fontsize=5)
# edges <-
#   create_edge_df(
#     from = c(1,2,3,4,4),
#     to = c(3,4,4,5,6))
# g <- create_graph(nodes_df=nodes, 
#                   edges_df=edges)%>%
#    add_global_graph_attrs(
#       attr = c("layout", "rankdir", "splines"),
#       value = c("dot", "TB", "false"),
#       attr_type = c("graph", "graph", "graph"))
# render_graph(g)
```

```{r CodeGraph}
####Documenting the code: 
# library(CodeDepends)
# sc = readScript("/home/rstudio/PhysiMineR/Questions/ImpedanceQues/NegImpBRAVO/NegativeImpedanceBRAVO.Rmd")
# g = makeVariableGraph( info =getInputs(sc))
# if(require(Rgraphviz))
#   edgemode(g) <- "directed"
# x <- layoutGraph(g, layoutType="neato")
# zz = layoutGraph(g)
# graph.par(list(nodes = list(fontsize = 100)))
# renderGraph(zz)
```

## Results


**$\color{red}{\text{I.Define the Statistical methods}}$.**

**eg** Clinical isolates of MRSP cases (n = 150) and methicillin-susceptible S. pseudintermedius (MSSP) controls (n = 133) and their corresponding host signalment and medical data covering the six months prior to staphylococcal isolation were analysed by multivariable logistic regression.

The identity of all MRSP isolates was confirmed through demonstration of S. intermedius-group specific nuc and mecA.

**$\color{red}{\text{I.Describe demographics}}$.**
The mean age was 57.3 ± 17 years, and 62.3% of the subjects were male. 
The age-adjusted incidence rates were 13.8 (non-lobar) and 4.9 (lobar) per 100,000 person-years.
**$\color{red}{\text{J.Then describe level one results}}$.**

**$\color{red}{\text{K.Then describe subset results}}$.**

**eg** In the final model, cats (compared to dogs, OR 18.5, 95% CI 1.8-188.0, P = 0.01), animals that had been
hospitalised (OR 104.4, 95% CI 21.3-511.6, P < 0.001), or visited veterinary clinics more frequently (>10 visits
OR 7.3, 95% CI 1.0-52.6, P = 0.049) and those that had received topical ear medication (OR 5.1, 95% CI 1.8-
14.9, P = 0.003) or glucocorticoids (OR 22.5, 95% CI 7.0-72.6, P < 0.001) were at higher risk of MRSP infection,
whereas S. pseudintermedius isolates from ears were more likely to belong to the MSSP group (OR 0.09, 95%
CI 0.03-0.34, P < 0.001).

**Choose your statistical analysis**


```{r Results}
######################################### Data analysis######################################### 
```

## Discussion

**$\color{red}{\text{L.Sentence 1: To be decided}}$.**

**$\color{red}{\text{M.Sentence 2: To be decided}}$.**

**$\color{red}{\text{N.Sentence 3: To be decided}}$.**
**eg** These results indicate an association of MRSP infection with veterinary clinic/hospital
settings and possibly with chronic skin disease.


```{r Discussion}
```

## Limitations
**$\color{red}{\text{O.Sentence 1: To be decided}}$.**
**eg** There was an unexpected lack of association between MRSP and antimicrobial therapy; this requires further investigation .(Lehner et al., 2014).

```{r Limitations}
```



##Full abstract examples 

Methicillin-resistant Staphylococcus pseudintermedius (MRSP) has emerged as a highly drug-resistant small animal
veterinary pathogen. Although often isolated from outpatients in veterinary clinics, there is concern that
MRSP follows a veterinary-hospital associated epidemiology. This study's objective was to identify risk factors for
MRSP infections in dogs and cats in Germany. Clinical isolates of MRSP cases (n = 150) and methicillin-susceptible
S. pseudintermedius (MSSP) controls (n = 133) and their corresponding host signalment and medical data
covering the six months prior to staphylococcal isolation were analysed by multivariable logistic regression. The
identity of all MRSP isolates was confirmed through demonstration of S. intermedius-group specific nuc and
mecA. In the final model, cats (compared to dogs, OR 18.5, 95% CI 1.8-188.0, P = 0.01), animals that had been
hospitalised (OR 104.4, 95% CI 21.3-511.6, P < 0.001), or visited veterinary clinics more frequently (>10 visits
OR 7.3, 95% CI 1.0-52.6, P = 0.049) and those that had received topical ear medication (OR 5.1, 95% CI 1.8-
14.9, P = 0.003) or glucocorticoids (OR 22.5, 95% CI 7.0-72.6, P < 0.001) were at higher risk of MRSP infection,
whereas S. pseudintermedius isolates from ears were more likely to belong to the MSSP group (OR 0.09, 95%
CI 0.03-0.34, P < 0.001). These results indicate an association of MRSP infection with veterinary clinic/hospital
settings and possibly with chronic skin disease. There was an unexpected lack of association between MRSP and antimicrobial therapy; this requires further investigation .(Lehner et al., 2014).

##Explanation
The abstract provides key information that enables readers to understand the key aspects of the study and decide
whether to read the article. In STROBE, item 1b recommended that authors provide an informative and balanced
summary of what experiments were done, what results were found and the implications of the findings in the abstract.
In STROBE-Vet, this item was modified to provide more guidance on the key components that should be addressed.
The study design should be stated; however, if the study does not correspond to a named study design such as case-
control, cross-sectional and cohort study, then the author should describe the key elements of the study design such
as incident versus prevalent cases, and whether or not the selection was based on outcome status (Pearce, 2012). The
abstract should succinctly describe the study objectives, including the primary objective and primary outcome, the
exposure(s) of interest, relevant population information such as species and the purpose (or uses) of the animals,
the study location and dates, and the number of study units. In addition, including the organizational level at
which the outcome was measured (e.g. herd, pen or individual) is recommended. The presented results should
include summary outcome measures (e.g. frequency or appropriate descriptor of central tendency such as mean or
median) and, if relevant, a clear description of the association direction along with accompanying association measures
(e.g. odds ratio) and measures of precision (e.g. 95% confidence interval) rather than P-value alone. We discourage
stating that an exposure is or is not significantly associated with an outcome without appropriate statistical
measures. Finally, because many veterinary observational studies evaluate multiple potential risk factors, the abstract
should provide the number of exposure-outcome associations tested to alert the end-user to potential type I error in
the study. When multiple outcomes are observed, provide the reader with a rationale for the outcomes presented in
the abstract, for example only statistically significant results or the outcome of the primary hypothesis is presented.






##Other examples of good abstracts:

 Lymphoma in patients treated with anti-TNF: results of the 3-year prospective French RATIO registry
 X Mariette1, F Tubach2, H Bagheri3, M Bardet4, J M Berthelot5, P Gaudin6, D Heresbach7, A Martin8, T
 Schaeverbeke9, D Salmon10, M Lemann11, O Hermine12, M Raphael13, P Ravaud2
 
 Author affiliations
 
 Abstract
 
 **Objective:** To describe cases of lymphoma associated with anti-TNF therapy, identify risk factors,
 estimate the incidence and compare the risks for different anti-TNF agents.

 **Methods:** A national prospective registry was designed (Research Axed on Tolerance of bIOtherapies; RATIO)
 to collect all cases of lymphoma in French patients receiving anti-TNF therapy from 2004 to 2006, whatever
 the indication. A case-control analysis was conducted including two controls treated with anti-TNF per case
 and an incidence study of lymphoma with the French population was used as the reference.

 **Results:** 38 cases of lymphoma, 31 non-Hodgkin's lymphoma (NHL) (26 B cell and five T cell), five Hodgkin's
 lymphoma (HL) and two Hodgkin's-like lymphoma were collected. Epstein-Barr virus was detected in both of two
 Hodgkin's-like lymphoma, three of five HL and one NHL. Patients receiving adalimumab or infliximab had a higher
 risk than those treated with etanercept: standardised incidence ratio (SIR) 4.1 (2.3-7.1) and 3.6 (2.3-5.6)
 versus 0.9 (0.4-1.8). The exposure to adalimumab or infliximab versus etanercept was an independent risk factor
 for lymphoma in the case-control study: odds ratio 4.7 (1.3-17.7) and 4.1 (1.4-12.5), respectively. The sex and
 age-adjusted incidence rate of lymphoma was 42.1 per 100 000 patient-years. The SIR was 2.4 (95% CI 1.7 to 3.2).

 **Conclusion:** The two to threefold increased risk of lymphoma in patients receiving anti-TNF therapy is similar
 to that expected for such patients with severe inflammatory diseases. Some lymphomas associated with
 immunosuppression may occur, and the risk of lymphoma is higher with monoclonal-antibody therapy than with
 soluble-receptor therapy.


 http://dx.doi.org/10.1136/ard.2009.117762


 Most studies investigating the association between psoriasis and cardiovascular disease
 have shown a significant relationship. This comparison study investigated the association
 between psoriasis and prevalent use of cardiovascular drugs. Drug exposure data for 1998 to
 2006 were extracted from the Dutch PHARMO-Record Linkage System database. Psoriasis patients were
 selected using an algorithm of hospitalization and drug dispensing records specific for psoriasis and
 matched with controls for gender, age and time-period. From the records of 2.5 million Dutch residents,
 9,804 (0.4%) psoriasis patients and 15,288 (0.6%) controls were selected. Psoriasis patients used
 significantly more anti-hypertensives, anti-coagulant and anti-platelet agents, digoxin, nitrates,
 lipid-lowering and anti-diabetic drugs than the reference population during a 5-year period observation.
 In a multiple linear regression model adjusting for the number of unique drugs used, psoriasis was no longer
 significantly associated with any of these drug classes. Psoriasis patients used more cardiovascular-related
 drugs, but surveillance bias appears to affect this association considerably.