---
title: "A good workman blames his tools. Understanding the contribution of endoscope model to the adenoma detection rate for experienced endoscopists"
author: "Sebastian Zeki PhD"
date: "27 June 2017"
output: word_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(readxl)
######################################### Data acquisiton######################################### 
final.df<-read_excel("S:\\Gastroenterology\\Seb\\R\\Data\\AdHoc//GSTT_GastroscopyProcedure2007_2017.xlsx")

######################################### Data merging######################################### 
#setwd("S:\\Gastroenterology\\Seb\\R\\Data\\SelfAudit\\OrigEndoscopyFrom2007ToApr1_2017")
#filenames <- list.files(pattern=".xlsx")
#library(plyr)
#df.list <- lapply(filenames, function(x) read.xlsx(x, sheet = 1, startRow = 1, colNames = TRUE))
#final.df <- rbind.fill(df.list)





######################################### Data cleaning######################################### 
source("S:\\Gastroenterology\\Seb\\R\\Scripts\\Generics\\CleanUp.R")
names(final.df)<-c("PatientID",  "NHSno", "PatientName", "birthdaynum","birthmonthnum" ,"birthyearnum" ,"Endo_ResultName", "Endo_ResultPerformed", "Endo_ResultEntered", "Endo_ResultText", "Histo_ResultName", "Histo_ResultPerformed", "Histo_ResultEntered", "Histo_ResultText")

final.df<-final.df[1:14]
final.df$Endo_ResultPerformed<-as.Date(final.df$Endo_ResultPerformed)
final.df$Endo_ResultEntered<-as.Date(final.df$Endo_ResultEntered)
final.df$Histo_ResultPerformed<-as.Date(final.df$Histo_ResultPerformed)
final.df$Histo_ResultEntered<-as.Date(final.df$Histo_ResultEntered)
final.df<-data.frame(final.df)
the_end<-nrow(final.df)
                                       ######################################### Data accordionisation#########################################
tryoutTBB<-final.df

#Had to split up and rebind as the data set is too big for the endoscopy function
final.df1<-EndoscChopper(final.df[1:20000,])
final.df2<-EndoscChopper(final.df[20001:40000,])
final.df3<-EndoscChopper(final.df[40001:60000,])
final.df4<-EndoscChopper(final.df[60001:80000,])
final.df5<-EndoscChopper(final.df[80001:100000,])
final.df6<-EndoscChopper(final.df[100001:the_end,])
final.df<-rbind(final.df1,final.df2)
final.df<-rbind(final.df,final.df3)
final.df<-rbind(final.df,final.df4)
final.df<-rbind(final.df,final.df5)
final.df<-rbind(final.df,final.df6)

#Get rid of pointless objects
rm(final.df1, final.df2, final.df3,final.df4)


final.df<-HistolChopper(final.df)

detach("package:plyr")


######################################### Data forking (filtering and subsetting)######################################### 
#1. All Filters should be numeric nrows and start with the term Fil_ appended to the nrow from which it is derived eg mydf becomes Fil_mydf<-nrow(mydf)
#Also need the original dataset that it comes from so data lineage is maintained
#Parent
Fil_final.df<-nrow(final.df)

#Children
OGDfinal.df<-final.df[grepl("Gastroscopy|Other",final.df$ProcPerformed),]
Fil_OGDfinal.df<-nrow(OGDfinal.df)
  #Grandchildren
  #BarrettsSurveillance
BarrettSurveillance<-OGDfinal.df[grepl("Surveillance",OGDfinal.df$IndicationsFroExamination),]
  
  #Eosinophilic Oesophagitis
Eosinoph<-OGDfinal.df[grepl("[Ee]osinoph",OGDfinal.df$Dx_Simplified),]
   
                #Great_Grandchildren
                Eosinoph_Dysphagia<-Eosinoph[grepl("Dysphagia",Eosinoph$IndicationsFroExamination),]
Colonfinal.df<-final.df[grepl("Colonoscopy",final.df$ProcPerformed),]
Fil_Colonfinal.df<-nrow(Colonfinal.df)

ERCPfinal.df<-final.df[grepl("ERCP",final.df$ProcPerformed),]
Fil_ERCPfinal.df<-nrow(ERCPfinal.df)

EUSfinal.df<-final.df[grepl("EUS",final.df$ProcPerformed),]
Fil_EUSfinal.df<-nrow(EUSfinal.df)

Sigmoidoscopyfinal.df<-final.df[grepl("Sigmoidoscopy",final.df$ProcPerformed),]
Fil_Sigmoidoscopyfinal.df<-nrow(Sigmoidoscopyfinal.df)
```

#Script organised according to the cornerstones of gastro data science:

#Surveillance by 

```{r setup, include=FALSE}

library(dplyr)
library(lubridate)
library(stringr)
######## All endoscopies for proportions #############

AllOGD_Dysphagia_OverTime<-OGDfinal.df %>% filter(str_detect(IndicationsFroExamination, 'Dysphagia'))
#As unique patients
MyFirstEndoscopy_AllDysphagics<-AllOGD_Dysphagia_OverTime %>%
  group_by(PatientID) %>%
  arrange(Endo_ResultEntered) %>%
  filter(row_number()==1)%>% 
  group_by(year=year(Endo_ResultEntered)) %>% 
  summarise(Number=n())
#Then group by year
MyFirstEndoscopy_AllDysphagics<-MyFirstEndoscopy_AllDysphagics[!is.na(MyFirstEndoscopy_AllDysphagics),]

######## Surveillance Barretts######## 

#Get overall number of endoscopies being performed by year:

#1. Barrett's surveillance- How many are we doing per month since 2007?
SurveillanceOverTime<-BarrettSurveillance %>% group_by(year=year(Endo_ResultEntered)) %>% summarise(Number=n())

library(ggplot2)
 SurveillanceOverTimePlot<-ggplot(SurveillanceOverTime,aes(year,Number))+
geom_bar(stat="identity")

######## Eosinophilic Oesophagitis######## 
EoE<-Eosinoph_Dysphagia %>% group_by(year=year(Endo_ResultEntered)) %>% summarise(Number=n())

#GGplot here to show overall burden on endoscopy
 EoEOverTimePlot<-ggplot(EoE,aes(year,Number))+
geom_bar(stat="identity")

#Individual patients with EoE ggplot:
#Get their first endoscopy here:
MyFirstEoEEndoscopy<-Eosinoph_Dysphagia %>%
  group_by(PatientID) %>%
  arrange(Endo_ResultEntered) %>%
  filter(row_number()==1)%>% 
  group_by(year=year(Endo_ResultEntered)) %>% 
  summarise(Number=n())

MyFirstEoEEndoscopy$year<-as.character(MyFirstEoEEndoscopy$year)
library(scales)
EoEOverTimePlot<-ggplot(MyFirstEoEEndoscopy,aes(year,Number))+
geom_bar(stat="identity")+
  theme_bw() +
  labs(title="Individual patients with eosinophilic eosophagitis with dysphagia as the endoscopic indication") +
  labs(x = "Year", y = "Number of patients (unique)") 


#Do as proportions of all dysphagics:
#Get rid of 2007 so EoE and AllOGD_Dysphagia_OverTime can have cbind
AllOGD_Dysphagia_OverTimev2<-MyFirstEndoscopy_AllDysphagics[!MyFirstEndoscopy_AllDysphagics$year==2007,]

#Do the cbind
PropEoE<-merge(MyFirstEoEEndoscopy,AllOGD_Dysphagia_OverTimev2,by=c("year"))
names(PropEoE)<-c("year","NumberEoE","NumberAllDysphagia")
PropEoE$Prop<-(PropEoE$NumberEoE/PropEoE$NumberAllDysphagia)*100

PropEoE$year<-as.character(PropEoE$year)
EoEOverTimePlot<-ggplot(PropEoE,aes(year,Prop))+
geom_bar(stat="identity")+
  theme_bw() +
  labs(title="% of unique patients with dysphagia who have eosinophilic eosophagitis (with dysphagia as the endoscopic indication; EoE as >15eosinophils/hpf") +
  labs(x = "Year", y = "% of all dysphagia patients") 


```

######## Quality ######## 

######## Yield ######## 





######## Aim
<http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:
  
  ## Method---Can I extract the comments from an r script to 
  #Data acquisition, cleaning and filtration goes here
  
  Data was acquired from retrospectively from hospital records. `r 1+1` (#Filter 1 here) barium swallow reports were analysed. High resolution manometry reports were then acquired and cross referenced with the barium swallow reports. (#Filter 2 here) HRM's with a barium study within 1 year of the barium were retained. Fundoplication and post therapy patients were excluded from the analysis. 


######################################### Data analysis######################################### 
    ```{r}
#Diseases of interest
numOGD<-nrow(OGDfinal.df)
CMV<-OGDfinal.df[grepl("[Cc]ytomeg|CMV",OGDfinal.df$DxRaw),]
(nrow(CMV)/(numOGD))*100
HSV<-OGDfinal.df[grepl("[Hh]erpes",OGDfinal.df$DxRaw),]
(nrow(HSV)/(numOGD))*100
Candid<-OGDfinal.df[grepl("[Cc]andid",OGDfinal.df$DxRaw),]
(nrow(Candid)/(numOGD))*100
Barr<-OGDfinal.df[grepl("[Bb]arr",OGDfinal.df$DxRaw),]
(nrow(Barr)/(numOGD))*100
EoE<-OGDfinal.df[grepl("[Ee]osinop",OGDfinal.df$DxRaw),]
(nrow(EoE)/(numOGD))*100
```

    
########################################### FILTER DOCUMENTATION #########################################



#Always start the filter with the data source document

```{r echo=FALSE}

    
library(DiagrammeR)
    #Create the labels for the DiagrammeR plot: Always append Lab_ prior to using the filter value eg Lab_Fil_OGD<-paste("The filter",Fil_OGD, sep = ": ")
    #Lab_Fil_Data1<-paste("The filter",Fil_Data1, sep = ": ")
    #Lab_Fil_Data2<-paste("The filter",Fil_Data2, sep = ": ")
    #Lab_Fil_Data3<-paste("The filter",Fil_Data3, sep = ": ")
    
    Lab_Fil_All.df<-paste("All",Fil_All.df, sep = ": ")
    Lab_Fil_OesophLab<-paste("OesophLab",Fil_OesophLab.df, sep = ": ")
Lab_Fil_Source<-"S:\\Gastroenterology\\Seb\\R\\Data\\PhysiologyHuddleData\\PhysiologyHuddleRetroSpec_AttendancesFromOP17P_BO_Report.xls"
   
    
    nodes <- create_nodes(nodes = c(Lab_Fil_Source,Lab_Fil_All.df,Lab_Fil_OesophLab),                     
                          label = TRUE,
                          fontsize = 55,
                          fontcolour = "White",
                          type = "lower",
                          style = "filled",
                          color = "aqua",
                          shape = c("circle"),
                          x = c(0,0,0,0,0),
                          y = c(600,300,0,-300,-600,-900))
    
    #This is the complicated part as you have to tie the labels up together
    edges <- create_edges(from = c(Lab_Fil_Source,Lab_Fil_All.df), 
                          to = c(Lab_Fil_All.df,Lab_Fil_OesophLab),
                          #rel = c(nrow(MyBariumDataAll), nrow(MyBariumDataSwall), nrow(MyBariumDataWithHRMAny), nrow(MyBariumDataWithHRMD)),
                          arrowhead = rep("normal", 60),
                          # color = c("red", "red", "red", "red", "red", "red"),
                          length = c(500,200,50,50),
                          fontsize = 55)
```

####What about adding the dataframe to the value that gets generated from code depends to automate a Sankey plot?




    
########################################### CODE DOCUMENTATION ############################################
```{r echo=FALSE}

library(CodeDepends)
sc = readScript("S:\\Gastroenterology\\Seb\\R\\Scripts\\Generics\\SandboxScript.Rmd")
g = makeVariableGraph( info =getInputs(sc))
if(require(Rgraphviz))
  plot(g)

```
